---
title: "Tennis Group Project"
author: "Samuel Stockman, Angie Gray, Jack Simons"
date: "10/12/2020"
always_allow_html: true
header-includes:
  - \usepackage{bm}
output:
  pdf_document: default
---
<!-- use this to change our working directory -->
```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = "../tennis_wta/rel_files/")
```

Let's first load in the relevant data (see `tennis.R`)
```{r}
file_list = list.files()
```

Now we want to compile the data into a better format. We need the input `variables` which should be equal to something of the form: `variables = c('surface', 'winner_id', 'loser_id', 'loser_age', 'winner_age')` - alternatively if it left blank then we will load all the variables
```{r}
load_data <- function(file_list, variables=FALSE) {
  no_files <- length(file_list)
  for (file_index in 1:no_files) {
    temp_file <- read.csv(file_list[[file_index]])
    if (class(variables)=="character") {
      temp_file <- subset(temp_file, select = variables)
    }
    if (file_index==1) {
      melted_files <- temp_file
    } else {
      melted_files <- rbind(melted_files, temp_file)
    }
  }
  return(melted_files)
}
```
Let's now use this function
```{r}
# variables <- c('surface', 'winner_id', 'loser_id', 'winner_age', 'loser_age')
my_data <- load_data(file_list)
```
Let's see what the data looks like
```{r}
head(my_data, 5)
```

Now, for the logistic regression. We need to create our $D=\{(\bm{x}_i,y_i)\}_{i=1}^{n}$ - we will start off very naively 
```{r}
trans_data_naive <- function(data_mat, features) {
  
  no_feats <- length(features)
  new_dat <- subset(data_mat, select = features) #select the relewvant features
  orig_rows <- nrow(new_dat) #number of orginal games (which we double)
  
  #flip the dataset
  for (i in 1:(no_feats/2)) {
    temp_df <- data.frame(new_dat[,(2*i)], new_dat[,(2*i-1)]) 
  }
  colnames(temp_df)=features
  new_dat <- rbind(new_dat, temp_df)
  
  #add the results
  new_dat$result <- c(rep(1,orig_rows), rep(-1, orig_rows))
  new_dat$result <- as.numeric(new_dat$result)
  
  #change the column names to reflect that we have added result column
  colnames(new_dat)[1:2] <- c("p1_hand", "p2_hand")
  
  #add the bias column
  new_dat$bias <- 1
  
  return(new_dat)
}
```
Now let's look at this data
```{r}
features <- c("winner_hand", "loser_hand")
new_dat <- trans_data_naive(my_data, features)
head(new_dat)
```
We notice that some people do not have a hand are are listed as "" or "U". **Let's choose to remove these from the data set.**
```{r}
new_dat <- new_dat[-which(new_dat$p1_hand=="U"),]
new_dat <- new_dat[-which(new_dat$p1_hand==""),]
new_dat <- new_dat[-which(new_dat$p2_hand=="U"),]
new_dat <- new_dat[-which(new_dat$p2_hand==""),]
unique(new_dat$p2_hand)
unique(new_dat$p1_hand)
```
Let's one hot encode this variable
```{r}
new_dat$p1_hand[which(new_dat$p1_hand=="L")] <- 0
new_dat$p1_hand[which(new_dat$p1_hand=="R")] <- 1
new_dat$p2_hand[which(new_dat$p2_hand=="L")] <- 0
new_dat$p2_hand[which(new_dat$p2_hand=="R")] <- 1
new_dat$p1_hand <- as.numeric(new_dat$p1_hand)
new_dat$p2_hand <- as.numeric(new_dat$p2_hand)
```
We need to separate $y$ and $\bm{x}$.
```{r}
y_dat <- subset(new_dat, select=result)
x_dat <- subset(new_dat, select=-result)
```

Let's make the logistic regression
```{r}
sigma_f <- function(t) {
  return(1/(1+exp(t)))
}

log_reg_naive <- function(w, x, y) {
  f <- as.matrix(x)%*%w
  return(-sum(log(sigma_f(f*y))))
}

log_reg_naive_grad <- function(w, x, y) {
  f <- as.matrix(x)%*%w
  temp <- rep(0,dim(x)[2])
  for (i in 1:dim(x)[2]) {
    temp[i] <- sum(sigma_f(f*y)*exp(f*y)*y*x[,i])
  }
  return(temp)
}

set.seed(2020) #random seed for reproducibility
w <- rnorm(3) #random initialization
log_reg_naive(w, x_dat, y_dat)
optim(rnorm(3), log_reg_naive, x=x_dat, y=y_dat, control=list(maxit=2000), gr=log_reg_naive_grad)
```




